---
title: "R Notebook"
output: html_notebook
author: "Jessica Teixeira Araujo"
---

    Step-by-step guide for performing the McNemar Test

Step 1: assuming a significance level of 5%, i.e., α = 0.05.

```{r}
alfa <- 0.05
print(alfa)
```
Step 2: considering a confidence level of 95%.

```{r}
confidence_level <- (1 - alpha) * 100
print(confidence_level)
```
Step 3: defining the degrees of freedom.

```{r}
df <- 1
print(df)
```
Step 4: finding the critical value for the chi-square distribution.

```{r}
critical_value <- qchisq(1 - alpha, df)
print(critical_value)
```
Step 5: constructing the vector containing the data from the conducted experiment.

```{r}
contingency_table <- matrix(c(37, 3, 13, 47), nrow = 2, byrow = TRUE)
print(contingency_table)
```
Passo 6: aplicando a função necessária para execução do teste → mcnemar.test

```{r}
mcnemar.test(contingency_table)
test_result <- mcnemar.test(contingency_table)
```
Passo 7: extraindo o p-valor para tomada de decisão por laço de código.

```{r}
p_value <- test_result$p.value
print(p_value)
```
Passo 8: tomando a decisão.

```{r}
if (p_value > alpha) {
  cat("Since the p-value is greater than α =", alpha, 
      ", there is not enough evidence to reject Ho at the confidence level of", confidence_level, "%.")
} else {
  cat("Since the p-value is less than α =", alpha, 
      ", there is enough evidence to reject Ho at the confidence level of", confidence_level, "%.")
}
```

