---
title: "R Notebook"
output: html_notebook
author: "Jessica Teixeira Araujo"
---

Step-by-step for performing the Wilcoxon Test

Step 1: Assuming a significance level of 5%, i.e., α = 0.05.
```{r}
alfa <- 0.05
print(alfa)
```
Step 2: Considering a confidence level of 95%.

```{r}
confidence_level <- (1 - alfa) * 100
print(confidence_level)
```

Step 3: Constructing the vector containing the experimental data.

```{r}
normal = c(1903, 1935, 1910,2496, 2108, 1961,2060, 1444, 1612, 1316, 1511)
print(normal)
dried = c(2009, 1915, 2011, 2463, 2180, 1925, 2122, 1482, 1542, 1443, 1535)
print(dried)
```
Step 4: Applying the function needed to perform the test → wilcox.test

Where:

normal and dried: are the groups being compared;

paired = TRUE: true for paired data;

alternative = c("two.sided"): is used for a two-tailed test.

```{r}
wilcox.test(normal, dried, paired = TRUE, alternative = c("two.sided"))
test_result <- wilcox.test(normal, dried, paired = TRUE, alternative = c("two.sided"))
```
Step 5: Extracting the p-value for decision making using code.

```{r}
p_value <- test_result$p.value
print(p_value)
```
Step 6: Making the decision.

```{r}
if (p_value > alfa) {
  cat("Since the p-value is greater than α =",alfa,", there is not enough evidence to reject Ho at the",confidence_level,"% confidence level.")
} else {
  cat("Since the p-value is less than α =",alfa,", there is enough evidence to reject Ho at the",confidence_level,"% confidence level.")
}
```

