---
title: "R Notebook"
output: html_notebook
author: "Jessica Teixeira Araujo"
---

    Step-by-step for performing the Binomial Test

Step 1: Assuming a significance level of 5%, i.e., α = 0.05.

```{r}
alfa <- 0.05
print(alfa)
```
Step 2: Considering a confidence level of 95%.

```{r}
confidence_level <- (1 - alfa) * 100
print(confidence_level)
```
Step 3: Applying the function needed to perform the test → binom.test

Where:

5: number of observed successes;

16: sample size;

p = 0.3: null hypothesis for 30%; and

alternative = c("greater"): greater is used for a right-tailed test.

```{r}
binom.test(5, 16, p=0.3, alternative = c("greater"), conf.level = 0.95)
test_result <- binom.test(5, 16, p=0.3, alternative = c("greater"), conf.level = 0.95)
```
Step 4: Extracting the p-value for decision making using code.

```{r}
p_value <- test_result$p.value
print(p_value)
```
Step 5: Making the decision.

```{r}
if (p_value > alfa) {
  cat("Since the p-value is greater than α =", alfa, ", there is not enough evidence to reject Ho at the", confidence_level, "% confidence level.")
} else {
  cat("Since the p-value is less than α =", alfa, ", there is enough evidence to reject Ho at the", confidence_level, "% confidence level.")
}
```