---
title: "R Notebook"
output: html_notebook
author: "Jessica Teixeira Araujo"
---

    Step-by-step for performing the Kolmogorov-Smirnov Test

Step 1: Assuming a significance level of 5%, i.e., α = 0.05.
```{r}
alfa <- 0.05
print(alfa)
```
Step 2: Considering a confidence level of 95%.

```{r}
nivel_de_confianca <- (1 - alfa) * 100
print(nivel_de_confianca)
```
Step 3: Constructing the vector containing the experimental data.

```{r}
k = c(15,25,10,5,4,1)
print(k)
```
Step 4: Applying the function needed to perform the test → ks.test

Where:

k: vector containing the data; and

"ppois", 1.2: represents the Poisson distribution with lambda equal to 1.2.

```{r}
ks.test(k, "ppois", 1.2)
test_result <- ks.test(k, "ppois", 1.2)
```

Step 5: Extracting the p-value for decision making using code.

```{r}
p_value <- test_result$p.value
print(p_value)
```
Step 6: Making the decision.

```{r}
if (p_value > alfa) {
  cat("Since the p-value is greater than α =",alfa,", there is not enough evidence to reject Ho at the",confidence_level,"% confidence level.")
} else {
  cat("Since the p-value is less than α =",alfa,", there is enough evidence to reject Ho at the",confidence_level,"% confidence level.")
}
```
